Adopting agile in the large: motivations, success factors and challenges

### 2014-04-07 journal/article.tex
Introduction paragraph

>>>>

This section presents the findings of the literature review. In the first
subsection a meta analysis of the analyzed papers is presented. In the
subsequent sections findings are presented organized according to the research
questions. The methods used for extracting the results were described in section
\ref{sec:method}.

\subsection{Summary of papers}
